### 2010-12-06 report/report.tex
intro edit

We are using machine learning to design a gait for a quadruped
robot. The code so far consists of the robot
class, optimization class, parameterized model, sine model, and camera
feedback.

>>>>

This paper presents a comparison of varied learning methods to
design a gait for a quadruped robot. Using these methods we have
created walks that are several times faster than the original
hand-tuned gait.
